%*******************************************************************************
%*********************************** Acknowledgements **************************
%*******************************************************************************

\chapter{Acknowledgments}
\label{chap:acknowledgements}

\noindent First and foremost, I want to thank my supervisors Hedvig Kjellström and Cheng Zhang for giving me the opportunity to pursue PhD studies. Hedvig, I admire your constant encouragement and curiosity, as well as your willingness to make everyone feel welcome around you. Cheng, I am forever grateful for every time you pulled me out of a rabbit hole, patched me up, and strengthened my self-confidence. You have motivated me to always aim high and do my utmost to become a better researcher. 
\newline


\noindent 
During my studies, I have proven to myself the importance of daring to ask for help, a courage I am still practicing to fully master. Along this line, I want to express my deepest gratitude to Patric Jensfelt for expanding my mind with motivating my research with challenges in the real-world.
Furthermore, I want to thank Henrik Götesson from The Swedish Association of the Visually Impaired (SRF) for enlightening me on the importance of involving the real target users in the development process of new technology. 
\newline 


\noindent 
I am unable to think of a better workplace for me than the division of Robotics, Perception, and Learning (RPL). %that would have been better for me, 
The faculty people there who have tried to teach me something play a major role in this feeling of mine. 
Firstly, I want to thank my mentor Iolanda Leite for all the advice to make me more at peace with myself during my studies. 
Mårten Björkman, thank you for all the tools and insights on teaching that you have provided me with, you have indeed motivated me to inspire people to learn more about computer vision. %indeed motivated me to search for opportunities where I get to inspire people to learn more about computer vision. 
John Folkesson, thank you for letting me help shape your course on probabilistic graphical models and for always considering the suggestions from us teaching assistants. Additionally, I want to thank 
Christian Smith for all the thoughtful brainteaser questions at the \%-seminars, 
Hossein Azizpour and Josephine Sullivan for changing my mindset on the possibilities of deep learning, 
and Atsuto Maki and Jana Tumova for their kindness toward me.  
\newline 


\noindent 
Thanks to my research group, I have become better at presenting my work and speaking about my ideas and thoughts. Therefore, I want to thank 
Sofia, 
Ruibo, 
Taras, 
Olga, 
Ci, 
Benjamin, 
Maheen, 
and Vincent
for maintaining a supportive environment with constructive feedback, fruitful discussions, and relaxing social activities in- and outside the office. 
I am dedicating an extra amount of gratitude to Sofia for all the conversations that often have given me insights on how I can express myself more clearly, and Ruibo, for his curiosity about what I am working on and advice on how to conduct valuable research. 
To have anything at all to present to the above-mentioned people, I must thank the RPL GPU cluster team members of Joonatan, Vladimir, Federico, Matteo, and Yonk, my research results would have taken a lot more time to find without you. 
\newline 

%I want to thank my research group with Sofia Broomé, Ruibo Tu, Taras Kucherenko, Olga Mikheeva, Ci Li, Benjamin Christoffersen, and Vincent Trichon, for maintaining a supportive environment with constructive feedback, fruitful discussions, and relaxing social activities in- and outside the office. Especially, I want to dedicate an extra amount of gratitude to Sofia for all the conversations that have often given me insights in how I can express myself more clearly, and Ruibo, for his kindness and advice on how to conduct valuable research.   


\noindent 
Although the past years have been challenging, I have been truly blessed with wonderful colleagues who have given me energy to continue my studies.  
Firstly, I want to thank Ciwan and Ignacio for being so easy to talk with about life in general, and for all the laughs at our own expenses that have given me new perspectives. 
Moreover, I am thankful to 
P\"{u}ren, 
Judith, 
Xi, 
Georg, 
Alexis, 
and Daniel for being such awesome office-mates. 
Thank you to Diogo and Silvia for their friendliness, I wish I had made the effort to get to know you earlier. 
And  
Jesper, 
Pouria, 
Fernando,
Sanne, 
Irmak,
and Sarah, with whom I have experienced two office re-locations, thank you for being so open and kind throughout our years together. 
Furthermore, I feel very fortunate for having gotten to know
Grace, 
Alex, 
Ioanna,
Wei,
Ilaria, 
Katie,
Marta, 
Fereidoon,
Matti, 
Chris, 
Teresa, 
Mart,
Arzu, 
Bastian, 
Gaspar, 
and José,
thank you for making me laugh so much during the last two years. 
\newline 

%I have joy to get to know Grace Hung, Alex Sleat, Ioanna Mitsioni, Ilaria Torre, Katie Winkle, Wei Wang, Marta Romeo, Chris Sprague, Matti Vahs, Mart Kartasev, Teresa Parreira, Fereidoon Zangeneh, Arzu Guneysu Ozgur, Bastian, Gaspar, and José. Although the past years have been challenging, all laughs I have had with you have made me endure this, thank you.


%It has been great to follow the progress of Jesper Karlsson, Pouria Tajvar, Fernando dos Santos Barbosa, Irmak Do\u{g}an, Sanne van Waveren, and Sarah Gillet, which I have experienced two moves at the KTH Campus together. At the final office stop, Lindstedtsvägen 24, I have joy to get to know Grace Hung, Alex Sleat, Ioanna Mitsioni, Ilaria Torre, Katie Winkle, Wei Wang, Marta Romeo, Chris Sprague, Matti Vahs, Mart Kartasev, Teresa Parreira, Fereidoon Zangeneh, Arzu Guneysu Ozgur, Bastian, Gaspar, and José. Although the past years have been challenging, all laughs I have had with you have made me endure this, thank you. 
%Ciwan Ceylan and Ignacio Torroba Balmori for being so easy to talk with about life in general and all the laughs that have taken the edge off the seriousness in many situations to give me perspective. All of you mentioned above have made it easier for me to write this thesis. 
%\newline 

\noindent 
I am immensely grateful that I have been rewarded with having Christian Pek and Truls Nyberg as both colleagues and friends.  
Christian, you have been like a big brother to me, always being there to help me out with any issue, and giving me advice on how to take care of my work and myself. 
Truls, I am so happy that our paths finally collided after so many years next to each other without knowing. I have enjoyed all of our schemes -- from far-fetched puns in the lunchroom to making Mora-Nisse shots at the party -- to bring joy into the room. 
%I will always be there for both of you. 
\newline 
%I have dedicated this paragraph to Christian Pek and Truls Nyberg, I am immensely grateful that I have been rewarded with friends like you two. 
%Christian, you have been like a big brother for me, always being there to help me out with any issue and give me advice on how to take care of my work and myself. Truls, I am so happy that our paths finally collided after so many years close by each other, and that we can discuss and laugh about matters at work and our lives. 


\noindent 
I want to show gratitude to Stefan Adalbjörnsson, S{\o}ren Vang Andersen, and Andreas Jakobsson, who were the first ones encouraging me to pursue PhD studies while I was writing my Master's thesis in Lund. %, since this thesis would have never been written without you. 
I am glad that my connection to Lund has stayed strong by keeping in touch with the now PhDs Gabrielle Flood, Lea Versbach, and Filip Elvander, whom I want to thank for their endless support and openness to share experiences and advice from their academic journeys. 
I also want to dedicate this thesis to my friends outside of academia,
%from my hometown Luleå and university town Lund, 
especially Jens, Nils, and William, for always being there for me regardless of how infrequently we meet. 
And Samuel, thank you for your honesty and caring for my well-being, I am so happy that our friendship was more than just being colleagues. 
\newline 

%, I want to thank Stefan Adalbjörnsson, S{\o}ren Vang Andersen, and Andreas Jakobsson in the first place who were the ones encouraging me to pursue a PhD while I was writing my Master's thesis in Lund. I also want to thank Filip Elvander for sharing his experiences while visiting Stockholm. 
%Finally, I want to thank my fellow Da Vinci PhD students Gabrielle Flood and Lea Versbach. I am so glad that we have stayed in touch and could share experiences from our academic journeys, thank you for all the advice on thesis writing. 


%\noindent I want to show my gratitude to my friends from my hometown Luleå and Lunds Tekniska Högskola, especially Jens, Nils, and William, for always being there for me regardless of how infrequently we meet. Samuel, I am so happy that our friendship was more than just being colleagues, and I am thankful for your honesty and sharing of your thoughts.   
%\newline    


\noindent Finally, I want to thank my closest family for their unyielding support and encouragement. To my father, Hans, thank you for reminding me that hard work pays off and that I sometimes just have to bite the bullet to get through. 
To my brother, Henrik, who always encourages me to walk towards places that I believe will make me happy, thank you for the tough love that makes me want to become a better person. 
To my mother, Ewa, for providing me with a stable ground to build my life on, thank you for motivating me to always do my best and reminding me that I should write more. 
To my dear Irene, thank you for being the solid rock that I can lean on anytime and anywhere. %in both bright and dark times. 
In my worst moments, you have been the one who calms me down and makes me feel that everything will work out in the end. 
I love you all.
%\noindent Finally, I want to thank my closest family. To my father, Hans, for reminding me that hard work pays off, and that I sometimes just have to bite the bullet. To my brother, Henrik, who have always encouraged me to walk towards places that I believe will make me happy, thank you for the tough love that makes me want to become a better person. To my mother, Ewa, for providing me with a stable ground to build my life on, thank you for motivating me to always do my best and reminding that I should write more. To my dear Irene, thank you for being the solid rock that I can lean on in both bright and dark times. In my worst moments, you are the one who calms me down and makes me feel that everything will work out in the end.
%\newline    




\begin{comment}
	\begin{itemize}
		\item Supervisors Hedvig and Cheng
		\item Patric Jensfelt for enlightening me about focusing on how things we develop and do research on should be used in the real-world in practice. "What happens if a blind person walks into the store, takes a photo of something and NOTHING WORKS?!"
		\item Internal reviewer (Danica Kragic?)
		\item Henrik Götesson (SRF) for the discussion on assistive vision tech in the fall 2020 to give me insights on how they are used by visually impaired people. 
		\item Disney internship Cheng, Rafael Tena, and Stephan Mandt for giving me the opportunity. Roommates and Denys
		\item Courses I got to TA Mårten Björkman, John Folkesson, Josephine Sullivan. Christian Smith for the thoughtful questions on various presentations. Hossein Azizpour for changing my mindset on the possibilities of deep learning.   
		\item RPL cluster team. Joonatan Määntäri, Vladimir Li, Federico B, Matteo Gamba, Yonk Shi. My research wouldn't have been possible without you, thank you. 
		\item To my group, Sofia, Ruibo, Taras, Olga, Ci. Extra to Benjamin for all good questions and chats. and Vincent. 
		\item To all my roommates; Judith, Puren, Xi, Samuel, Sofia, Maheen, Ci, Georg, Alexis, Truls, Christian, and Daniel
		\item To Chris, Truls, Ciwan, Ignacio
		\item To Lv24 and shoutout to Tr14. 
		\item Samuel, I am happy that our friendship was more than just colleagues. I am thankful for sharing your thoughts on machine learning.  
		\item To my fellow Da Vinci phds, Lea and Gabrielle. To Filip Elvander. To Stefan Adalbjörnsson, Söran Vang Andersen, Johan Swärd and Andreas Jakobsson for the encouraging and helpful environment you let me be part of during my Master's thesis in 2015-2016. Especially, Stefan, Sören, and Andreas for encouraging me to pursue research. 
		\item To my Lund friends, especially William
		\item To my Luleå friends, especially Jens and Nils
		\item To my family and Irene
	\end{itemize}
\end{comment}